### 2022-04-06 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@b3e97c387fcd2d3bb3787550a5e90c67f911bbe2 🚀

We downloaded the βCoV reservoir database from
https://www.viralemergence.org/betacov on Aug.~2021. This database was
assembled by a combination of data mining, literature surveys, and
application of an ensemble recommender system classifying hosts as
either ``Suspected'' or ``Unlikely'' (REF BECKER). The hosts considered
for this study were all hosts with a known record of a betacoronavirus,
and all those with a ``Suspected'' status in the ensemble model. This
resulted in a list of TK TP unique host species.

@@

>>>>

We downloaded the data on bats hosts of betacoronaviruses assembled by
Becker et al. (2022) from
\texttt{https://www.viralemergence.org/betacov} on Aug.~2021, and
filtered it to ``known'' hosts (established before the emergence of
SARS-CoV-2) and ``novel'' hosts (confirmed through sampling since the
emergence of SARS-CoV-2). This database was assembled by a combination
of data mining and literature surveys.

@@

\leavevmode\hypertarget{ref-Becker2022OptPre}{}%
Becker, D. J. et al. 2022. Optimising predictive models to prioritise
viral discovery in zoonotic reservoirs. - The Lancet Microbe in press.
